Differentially Private Bayesian Inference

### 2018-06-19 main.tex
adjust figure location
fix location

\subsubsection{Based on Hellinger Distance}
\label{subsec_accuracy_hellinger}
% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
%     \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
%   \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
%     \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
% \caption{The experimental results of accuracy of four algorithms}
% \label{fig_data}
% \end{center}
% \end{figure*}
We first analyzed the accuracy based on the Hellinger distance. By repeating the experiments for 10000 times and plotting the accuracy after each execution, we got two groups of results under different parameters setting as in Fig. \ref{fig_beta_hellinger} and Fig. \ref{fig_dirichlet_hellinger}. X-axis is labeled with different mechanisms. We took four mechanisms in our experiments: our newly designed exponential mechanism with smooth sensitivity named ``ExpoMech of SS'', exponential mechanism with local sensitivity named `` ExpoMech of LS'', exponential mechanism with global sensitivity named `` ExpoMech of GS'' and Laplace mechanism named ``LaplaceMech''. Y-axis is the accuracy measured by Hellinger distance between output $r$ of each execution and the correct inference result $\bysinfer(x)$, $\hlg(r, \bysinfer(x))$.

\begin{figure*}
\begin{center}
\centering
  \subfigure[Data size $n = 500$ with global $\epsilon = 0.5$]{
    \includegraphics[width=0.48\textwidth]{accuracy_box_2.eps}}
  \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
    \includegraphics[width=0.48\textwidth]{accuracy_box_1.eps}} 
\caption{The experimental results of accuracy of algorithms with Beta prior distribution $\betad(7,4)$ based on Hellinger distance}
\label{fig_beta_hellinger}
\end{center}
\end{figure*}
When prior distribution is $\betad$, under data size $n = 500$ and $300$, we obtained two plots in Fig. \ref{fig_beta_hellinger}. It is shown that our ExpoMech of SS is slightly better than Laplace mechanism and much more better than it with global sensitivity.

To have more experimental results, we then extended the $\betad$ to the $\dirichlet$ distribution as well as increased the data size, plotted in Fig. \ref{fig_dirichlet_hellinger}.
\begin{figure*}
\begin{center}
\centering
  \subfigure[Data size $n = 100$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.08 is Non-Private and with 0.0699407108115 - bound smooth sensitivity 0.09 is (0.8,0.8)-DP]{
    \includegraphics[width=0.48\textwidth]{accuracy_dirichlet_hellinger_1.eps}}
  \subfigure[Data size $n = 120$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP]{
    \includegraphics[width=0.48\textwidth]{accuracy_dirichlet_hellinger_2.eps}} 
\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance}
\label{fig_dirichlet_hellinger}
\end{center}
\end{figure*}

@@

Subfigs (a) are from Sec. \ref{subsec_accuracy_hellinger} shows the average accuracy of these mechanisms by executing them for 10000 times. x-axis is labeled with mechanisms and y-axis is the accuracy of every execution outputs measured by Hellinegr distance. Subfigs (b) are concrete probabilities of Laplace and our exponential mechanisms' wrt. the steps. x-axis is the hellinger distance from correct answer, i.e. steps from correct answer. Since they have the same meaning, here we just use the hellinger distance to label the x-axis. The y-axis is the probability of output candidates with corresponding steps (i.e. Hellinger distance) from correct answer.

>>>>

\subsubsection{Based on Hellinger Distance}
\label{subsec_accuracy_hellinger}
% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
%     \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
%   \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
%     \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
% \caption{The experimental results of accuracy of four algorithms}
% \label{fig_data}
% \end{center}
% \end{figure*}

\begin{figure*}
\begin{center}
\centering
  \subfigure[Data size $n = 500$ with global $\epsilon = 0.5$]{
    \includegraphics[width=0.48\textwidth]{accuracy_box_2.eps}}
  \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
    \includegraphics[width=0.48\textwidth]{accuracy_box_1.eps}} 
\caption{The experimental results of accuracy of algorithms with Beta prior distribution $\betad(7,4)$ based on Hellinger distance}
\label{fig_beta_hellinger}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\centering
  \subfigure[Data size $n = 100$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.08 is Non-Private and with 0.0699407108115 - bound smooth sensitivity 0.09 is (0.8,0.8)-DP]{
    \includegraphics[width=0.48\textwidth]{accuracy_dirichlet_hellinger_1.eps}}
  \subfigure[Data size $n = 120$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP]{
    \includegraphics[width=0.48\textwidth]{accuracy_dirichlet_hellinger_2.eps}} 
\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance}
\label{fig_dirichlet_hellinger}
\end{center}
\end{figure*}

We first analyzed the accuracy based on the Hellinger distance. By repeating the experiments for 10000 times and plotting the accuracy after each execution, we got two groups of results under different parameters setting as in Fig. \ref{fig_beta_hellinger} and Fig. \ref{fig_dirichlet_hellinger}. X-axis is labeled with different mechanisms. We took four mechanisms in our experiments: our newly designed exponential mechanism with smooth sensitivity named ``ExpoMech of SS'', exponential mechanism with local sensitivity named `` ExpoMech of LS'', exponential mechanism with global sensitivity named `` ExpoMech of GS'' and Laplace mechanism named ``LaplaceMech''. Y-axis is the accuracy measured by Hellinger distance between output $r$ of each execution and the correct inference result $\bysinfer(x)$, $\hlg(r, \bysinfer(x))$.

When prior distribution is $\betad$, under data size $n = 500$ and $300$, we obtained two plots in Fig. \ref{fig_beta_hellinger}. It is shown that our ExpoMech of SS is slightly better than Laplace mechanism and much more better than it with global sensitivity.

To have more experimental results, we then extended the $\betad$ to the $\dirichlet$ distribution as well as increased the data size, plotted in Fig. \ref{fig_dirichlet_hellinger}.

@@

Subfigs (a) are from Sec. \ref{subsec_accuracy_hellinger} shows the average accuracy of these mechanisms by executing them for 10000 times. x-axis is labeled with mechanisms and y-axis is the accuracy of every execution outputs measured by Hellinegr distance. Subfigs (b) are concrete probabilities of Laplace and our exponential mechanisms' wrt. the steps. x-axis is the Hellinger distance from correct answer, i.e. steps from correct answer. Since they have the same meaning, here we just use the Hellinger distance to label the x-axis. The y-axis is the probability of output candidates with corresponding steps (i.e. Hellinger distance) from correct answer.
